---
title: "Homework 1"
author: "Yan Song"
output: github_document
---

This is my solution to HW1.

```{r setup, include FALSE}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

We can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

## Problem 2

First, we load the _penguins_ dataset:

```{r}

data("penguins", package = "palmerpenguins")

```

The data was collected on the islands includes `r unique(penguins$island)` in the following years: `r unique(penguins$year)` and the species includes `r unique(penguins$species)`. The dataset includes the following variables: `r ls(penguins)` with `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The penguin with the longest bill length is a Gentoo penguin from Biscoe Island with a bill length of `r max(pull(penguins,bill_length_mm), na.rm = TRUE) `mm while the the penguin with shortest bill length is an Adelie penguin from Dream Island with a bill length of `r min(pull(penguins,bill_length_mm), na.rm = TRUE) `mm. The mean bill length for all penguins in the dataset is `r round(mean(pull(penguins,bill_length_mm), na.rm = TRUE), digits = 2)` mm with the standard deviation of `r round(sd(pull(penguins,bill_length_mm), na.rm = TRUE), digits = 2)` mm. 

* The penguin with the maximum and minimum bill depth are an Adelie penguin form Torgersen Island and a Gentoo penguin from Biscoe Island with the bill depths of `r max(pull(penguins,bill_depth_mm), na.rm = TRUE) `mm and `r min(pull(penguins,bill_depth_mm), na.rm = TRUE) `mm respectively. The mean bill depth for all penguins in the dataset is `r round(mean(pull(penguins,bill_depth_mm), na.rm = TRUE), digits = 2)` mm with the standard deviation of `r round(sd(pull(penguins,bill_depth_mm), na.rm = TRUE), digits = 2)` mm. 

* The penguin with the longest flipper length is a Gentoo penguin from Biscoe Island with a flipper length of `r max(pull(penguins,flipper_length_mm), na.rm = TRUE) `mm while the the penguin with shortest flipper length is an Adelie penguin from Biscoe Island with a bill length of `r min(pull(penguins,flipper_length_mm), na.rm = TRUE) `mm. The mean flipper length for all penguins in the dataset is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)` mm with the standard deviation of `r round(sd(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)` mm. 

* The heaviest penguin is a Gentoo penguin from Biscoe Island with a mass of `r max(pull(penguins, body_mass_g), na.rm = TRUE) `g while the lightest penguin is a Chinstrap penguin from Dream Island with a bill length of `r min(pull(penguins,body_mass_g), na.rm = TRUE) `g. The mean body mass of all penguins in the dataset is `r round(mean(pull(penguins, body_mass_g), na.rm = TRUE), digits = 2)` g with the standard deviation of `r round(sd(pull(penguins,  body_mass_g), na.rm = TRUE), digits = 2)` g. 

Next we show a scatterplot of flipper_length_mm (y) vs bill_length_mm (x):

```{r warning=FALSE, message=FALSE}

ggplot(data=penguins,
       aes(x = bill_length_mm,
           y = flipper_length_mm,
           color = species)) + geom_point()

```

Finally we save the code to the file:
```{r warning=FALSE, message=FALSE}

ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)

```